MCTS Applied to Co-operative Problems

### 2015-08-04 Report/response.tex

\subsection{Review 2 (Reviewer D)}
\paragraph*{\textit{The writing is generally good, I only noticed one actual error "GGP[3]", but the tone is casual and a lot of inappropriately subjective comments are made}}
\paragraph*{\textit{The authors make a few dubious claims in the Introduction. GGP is not exactly "the field of writing Artificial Intelligence (AI) agents", and it is wrong to say that "MCTS doesn't requuire any knowledge about the game itself in order to play", as it needs to know starting position, legal moves, terminal states, etc. Perhaps the authors means "strategic knowledge". }}
Have clarified the definition of GGP with reference to this paper\cite{genesereth2005general} and the terminology used to define MCTS use of knowledge. 

@@

\paragraph*{\textit{The authors claim that MCTS works best when it is given rewards frequently. What is the evidence for this claim?}}
Have rewritten this to point out that MCTS can't provide anything but random if it isn't given enough time or depth to search to a state that provides a reward.

### 2015-08-04 Report/ceec.tex
Clarified the frequent rewards issue

Standard \gls{mcts} plays best when it is either able to search to the end of the game tree, or is given rewards frequently. \gls{mcts} tends to stumble when the time given to it isn't sufficient to allow it to locate any sequence of actions that provides a reward in order to differentiate the root's children \cite{perez2012monte}.

>>>>

Standard \gls{mcts} plays best when it is able to search far enough to locate states that provide a reward. \gls{mcts} tends to stumble when the time or search depth limit given to it isn't sufficient to allow it to locate any sequence of actions that provides a reward in order to differentiate the root's children \cite{perez2012monte}. When \gls{mcts} can't find any single state that contained a reward, all children of the node will contain identical values and the algorithm will be forced to make a random choice.
